---
title: "Week 1"
author: "VijayUpadhyay"
date: "14 October 2016"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown



```{r cars}
summary(cars)
```

## Matrix Operation Exercises

### Exercise1:

Suppose X is a matrix in R. Which of the following is NOT equivalent to X?

1) t(t(X))
2) X %*% matrix(1, ncol(X))
3) X*1
4) X %*% diag(ncol(X))


```{r}
x <- 1:3
X <- rbind(x, 2*x, 3*x)

t(t(X))

X %*% matrix(1, ncol(X))    #out of all the option this expression is not equivalant to X

X*1

X %*% diag(ncol(X))
```


### Exercise 2:

Solve the following system of equations using R:

3a + 4b - 5c + d = 10

2a + 2b + 2c - d = 5

a -b + 5c - 5d = 7

5a + d = 4

What is the solution for c:

```{r}

theta1 <- c(3, 4, -5, 1)
theta2 <- c(2, 2, 2, -1)
theta3 <- c(1, -1, 5, -5)
theta4 <- c(5, 0, 0, 1)

theta <- rbind(theta1, theta2, theta3, theta4)

y <- c(10, 5, 7, 4)
Y <- matrix(y, nrow = 4)

solution <- solve(theta) %*% Y

solution
a <- Y[1,1]
b <- Y[2,1]
c <- Y[3,1]
d <- Y[4,1]

```



Load the following two matrices into R:

a <- matrix(1:12, nrow=4)

b <- matrix(1:15, nrow=3)

Note the dimension of 'a' and the dimension of 'b'.

In the question below, we will use the matrix multiplication operator in R, %*%, to multiply these two matrices.

```{r}

a <- matrix(1:12, nrow=4)
b <- matrix(1:15, nrow=3)

```

### Exercise 3:

What is the value in the 3rd row and the 2nd column of the matrix product of 'a' and 'b'

```{r}

prodMatrix <- a %*% b
value <- prodMatrix[3, 2]

```

### Exercise 4:

Multiply the 3rd row of 'a' with the 2nd column of 'b', using the element-wise vector multiplication with *.
What is the sum of the elements in the resulting vector?

```{r}

mult <- a[3,] * b[,2]
sum(mult)

```
